### 2019-08-20 Writeup/Thesis/chapters/research_question.tex
Changes; - Added some changes from supervisor - Began fixing structure of the document

    \caption{Most recent RFC security recommendation}
    \label{fig:trustwordsNum}
\end{figure}
\end{center}
By sampling the \pep documentation they have defined the use case of the Trustword handshake: \textit{``A handshake is done by comparing the Trustwords between two users through a separate communication channel (e.g. in person or by phone)''.}\footnote{https://www.pep.security/docs/general\_information.html\#handshake}. It can be assumed due to the increased globalizatiohat is the time andn of the planet that the most common handshake occurrence is over the phone, and, therefore, not in person. This is the assumed context of the handshake. This means, to create near-matches, the similarity of words is quantified phonetically instead of visually.

>>>>

    \caption{Most recent RFC security recommendation}
    \label{fig:trustwordsNum}
\end{figure}
\end{center}
By sampling the \pep documentation they have defined the use case of the Trustword handshake: \textit{``A handshake is done by comparing the Trustwords between two users through a separate communication channel (e.g. in person or by phone)''.}\footnote{https://www.pep.security/docs/general\_information.html\#handshake}. It can be assumed due to the increased globalization of the planet that the most common handshake occurrence is over the phone, and, therefore, not in person. This is the assumed context of the handshake. This means, to create near-matches, the similarity of words is quantified phonetically instead of visually.
